Structured Versus Decorated Cospans

### 2020-12-23 cospans.tex
fixed three things related to units - see comments marked "jb"

Moreover, the monoidal unit $I_1$ for $F\lCsp_1$ is \cref{eq:monoidalunitFCsp}, given by the identity cospan $0_\A \rightarrow 0_\A \leftarrow 0_\A$ on the monoidal unit of $\A$ together with the trivial decoration $\bot_{0_\A} = \phi_0 \colon 1 \to F(0_\A)$ on $0_\A$, and the monoidal unit for the category of arrows of ${ _L \lCsp(\inta F)}$ is given by $(0_\A,\bot_{0_\A}) \rightarrow (0_\A,\bot_{0_\A}) \leftarrow (0_\A,\bot_{0_\A})$. This is mapped under $\lE$ again to the identity cospan on $0_\A$ with the trivial decoration on its apex, so $\lE_1$ strictly preserves the monoidal unit.   %%% Now it's really the identity!  Can we shorten this calculation, now that it actually works?   It's not so interesting now that it works.  - jb

>>>>

Moreover, the monoidal unit $I_1$ for $F\lCsp_1$, given by \cref{eq:monoidalunitFCsp}, is mapped under $\lE_1$ to the identity cospan on $0_\A$ with the trivial decoration on its apex, so $\lE_1$ strictly preserves the monoidal unit.   %%% Under our new assumptions it's really true! - jb
